### 2024-03-06 Scripts/Appendix_scripts/Appendix_pre-reg_analyses.Rmd
added (suggested) changes to methods section, and made the first appendix containing additional models and results.

---
title             : "The Impact of Measurement Practices and Measurement Error on Construct Validity and Replication Outcomes in Psychological Science"
shorttitle        : "Measurement Quality and Replicability"

author: 
  - name          : "Goos, C."
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Professor Cobbenhagenlaan 125, 5037 DB, Tilburg, The Netherlands"
    email         : "casgoos99@gmail.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Data curation"
      - "Formal Analysis"
      - "Investigation"
      - "Methodology"
      - "Visualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Nuijten, M.B."
    affiliation   : "1"
    role:
      - "Project Administration"
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Tilburg University"

authornote: |
  1 Department of Methodology and Statistics, Tilburg School of Social and Behavioral Sciences, Tilburg University, Tilburg, NL.

  Enter author note here. Caspar/Jelte/Marjan?

abstract: |
  Recently, the influence of measurement related issues on replicability has received more investigations. 
  In particular, studies have indicated that low reliability, and poor measurement reporting can negatively influence the replicability of an effect. 
  Building on this new line of research, this study assessed these influences in large scale replication projects. 
  Protocols from the Many Labs replication projects, and the original articles that the replications were based on were used to assess the  reporting of the measures, while publicly available data from the Many Labs replications was used to assess the reliability of the measures. Reliability did not relate to replicability, and was generally consistent between labs for each measure in the Many Labs projects. 
  The quality of measurement reporting in replication protocols did however relate to replicability.
  Additionally, tentative evidence was found for a relation between quality of measurement reporting in the protocol of a replication and the quality of measurement reporting in its related original study.
  Recommendations are given for researchers and replicators in order to improve measurement practices in replication, and ward its negative impact on replicability. 
  Additionally, directions are given for future research investigating the relationship between measurement issues and replicability.

keywords          : "reliability, measurement, measurement reporting, replicability, construct validity"
wordcount         : "194"

bibliography      : ["r-references.bib", "references.bib"]

floatsintext      : yes
linenumbers       : no
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
knit              : worcs::cite_all
bibliography: references.bib
---

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(tidyr)
library(betareg)
library(lmerTest)
library(psych)
library(forcats)
library(GPArotation)
library(ggplot2)
library(ggridges)
library(GGally)
library(ggforce)
library(grid)
library(gridExtra)
library(metafor)

# loading source script
source(file = "C:/Users/u686785/OneDrive - Tilburg University/Documents/uvt/PHD/Master Thesis to Paper/Reproducible_R_Project/Scripts/source_script.R")

# Code below loads the processed data. The raw data was prepared for analysis in 'prepare_data.R.
load_data()

# creates a reference list for all used R packages and the installed R version (does not automatically include Rstudio)
r_refs("r-references.bib")

# manually retrieving the Rstudio version
rstudioapi::versionInfo()
```

<!-- altering latex defaults to get better figure and table placement -->

\renewcommand{\arraystretch}{0.7}

<!-- reducing the line spacing within tables -->

\renewcommand{\topfraction}{.85}

<!-- max fraction of page for floats at top -->

\renewcommand{\bottomfraction}{.7}

<!-- max fraction of page for floats at bottom -->

\renewcommand{\textfraction}{.15}

<!-- min fraction of page for text -->

\renewcommand{\floatpagefraction}{.66}

<!-- min fraction of page that should have floats -->

\setcounter{topnumber}{3} <!-- max number of floats at top of page --> \setcounter{bottomnumber}{3} <!-- max number of floats at bottom of page --> \setcounter{totalnumber}{4} <!-- max number of floats on a page --> <!-- remember to use [htp] or [htpb] for placement -->

@@

# Introduction

For many years, methodologists and statisticians have raised concerns about the way that research practices [@cumming2014new; @wicherts2016degrees], reporting practices [@bakker2011mis; @nuijten2016prevalence], and publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science] may undermine the credibility of psychology's scientific claims. Replicability of a finding is seen as one crucial step in establishing its credibility [@nosek2022replicability]. In order to investigate the replicability of psychological science, the large scale Reproducibility Project: Psychology (RPP) was set-up [@osc2015estimating]. Replications of 100 published studies were performed using similar materials, procedures, and analyses, while using a new sample of participants for each study. They found however, that in many instances the results did no match those of the original studies. This lack of replicability of psychological findings illustrated that psychology was facing a so-called 'replication crisis' [@hughes2018psychology; @giner2019crisis].

As a response, the demand to verify the credibility of psychological findings through replications rose. In order to attempt replications of various psychological findings, numerous large scale projects were set-up [@klein2014investigating; @camerer2016evaluating; @camerer2018evaluating; @ebersole2016many; @ebersole2020many; @klein2018many; @klein2022many]. Among these were the Many Labs projects, which operated similarly to the RPP, with the additional feature that each original article was replicated multiple times across different labs in various locations around the world. The results from these replication projects generally showed smaller effects than those reported in the original studies. Similarly, effects that had reached statistical significance in the original no longer did across the aggregate results of its replications.

Several explanations for this discrepancy between original and replication findings have been suggested and investigated, with many being centred around the concept of Questionable Research Practices [QRPs, @john2012measuring]. QRPs are practices, which either misrepresent or omit essential methodological information that is necessary for the evaluation of the research. Without this information, a reader will not know whether the result was in line with the author's expectation or simply the result of repeated trial and error until a suitable result was found [@simmons2011false]. Consequently, much of the discourse and the subsequent proposed solutions have been centred around preventing these QRPs through increased transparency in scientific reporting.

However, many researchers have also raised concerns that other factors, such as low power [@stanley2018what], lack of strong theoretical foundations [@eronen2021theory], and validity [@finkel2017replicability], which have not been given as much attention, are just as if not more responsible for the lack of successful replications found in psychology. An idea which has gained more traction recently is that measurement related issues have a large problematic influence on replicability. In particular, studies have focused on the effects of issues such as measurement error and questionable measurement practices on replicability [@stanley2014expectations; @shaw2020measurement; @flake2017construct; @flake2020measurement].

Measurement in psychological science is defined in large part by one overarching issue: psychological constructs, such as affective state and intelligence, cannot be measured directly. As a result, psychologists face two primary challenges in the use of measurement: First of all, the measure has to assess the construct it intends to measure, even though it can only do so indirectly. Secondly, because the measurement is indirect, it also comes with some degree of error surrounding its assessment of the construct. The first issue relates to the concept of validity, and specifically construct validity. Validity refers to the overall extent to which a measure measures what it is supposed to [@borsboom2004concept], while construct validity specifically refers to the substantial relation between the item scores on a psychological measure and the psychological construct it intends to measure. In order for indirect assessment of psychological constructs to be a viable approach, the measure needs to have construct validity [@cook2002experimental]. The second issue relates to the concept of measurement error and reliability. Measurement error indicates the amount of variation in item scores that is the result of the used measures inaccuracies, and not due to differences in the underlying psychological construct of interest.

@stanley2014expectations demonstrated, using a simulation study, the impact measurement error has on attempts to verify or falsify findings. Scalar item data was generated based on levels of sampling error and score-reliability, as the inverse of measurement error, that mimicked what is standard in psychological research, to ensure that the resulting degree of error was representative. The results indicated that measurement error caused observed effects found in replication research to vary heavily. ???relation measurement error and replicability (As a result, interpretations of replications might not be based on tests of the true effect, if the impact of measurement error is not attenuated for.)???

Another key aspect in evaluating the use of measures is how they are reported. Questionable Measurement Practices (QMPs) have been coined as a conjugate term to QRPs. QMPs are practices that decrease the information necessary to evaluate the measurement of a study. They range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement]. When this information is missing, it becomes difficult to establish that original and replication are measuring the same construct(s), which has detrimental consequences for direct replication attempts.

This study aims to investigate the influence of measurement error and QMPs on replicability, using data and reports from the large scale Many Labs replication projects. One goal is to expand the research by [@stanley2014expectations] with a practical example. Whereas they obtained their findings using a simulation study, this study investigated the scope of their findings in practice. QMPs in the context of replication research were already investigated by [@flake2022construct]. However, the investigations remained mostly descriptive. This study aims to expand upon the findings of [@flake2022construct] through the use of a new set of replication data, and by investigating the relation between QMP and replicability.

## Measurement Error

???connection/throughline of the measurement error hypotheses and other (including measurement error) hypotheses –\> is there a way to rewrite this part of the article to fit better as support/precedence to the QMP stuff???? –\> risky use of measurement!?!

As a first step it is worth investigating what the state of measurement error is in original and replication research in psychology, in order to assess the scope of @stanley2014expectations's findings in practice. Thus, this study investigated the following:

-   RQ1a. What is the degree of score reliability in replications of psychological research?

-   RQ1b. What is the degree of score reliability in original psychological research?

Since direct replications intend to investigate effects in nearly identical scenarios with nearly identical measures as the original study, it is expected that measurement errors are as present in replication research as in original psychological research.

-   H1. No difference is present in the degree of score reliability between replication research and original psychological research.

While reliability estimates are generally considered a measure specific feature, this is false. They are context dependent, and as a result the estimates of an effect can differ across contexts [@cho2015cronbach; @pauly2018resampling]. With large enough differences across contexts, the effect estimates between different replication attempts could deviate from each other beyond direct comparison. ???RELIABILITY VARIANCE IN META ANALYSIS???. To investigate this potential problem, the variation in score reliability is assessed for each measure when used in different contexts.

-   RQ2. To what degree do reliability estimates differ within a replication set of the same original study?

Even though reliability estimates are context dependent, sufficient protocol structure can counteract the variance in reliability estimates. An example of the standardising impact a structured protocol can have on reducing variability within an effect can be found in investigations into the closely related issue of heterogeneity [@patacchini2007unobserved]. Heterogeneity refers to the true variation in the true effect size due to minor but key differences in context, environment, and procedure. Heterogeneity is yet another proposed explanation for failed replications. This concern even prompted a Many Labs centred around the testing of heterogeneity in replications [@klein2018many]. However analyses from Many Labs 2, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects among replications. These findings demonstrate that it is possible to reduce variability as the result of context using structured protocols, as was done in the Many Labs projects this study analyzed.

-   H2. There is no significant variation in the reliability estimates of replications of the same original study.

This study investigated whether there is something in the measures used for replicated findings that sets them apart from those used for non-replicated findings. In particular, this study extends research by @stanley2014expectations on the relationship between reliability and replicability, by using data from real life replication projects.

-   RQ3. What is the association between replication study score reliability and replication outcome?

Greater score-reliability means greater consistency in estimation as variance around the estimate of the true effect is decreased. Consequently measures across different occasions, including between original and replication, should also become more consistent [@nunnaly1994assessment]. When original and replication research share consistent result, and as long as the studied effect is true, then on average their statistical conclusions should converge.

-   H3. Score reliability in replication research is positively associated with successful replication of an original finding.

Validity of measures can be assessed not only through features found in the data. The measure must also be chosen and implemented in a way that enables proper measurement of the variables [@flake2020measurement]. Any scientific report should therefore clearly motivate the measure and procedure that was used. Without clear reporting on these aspects, the validity of measurement will remain uncertain. Therefore, the other tests of this paper focused on the reporting aspects of measurement, assessed through QMPs.

## Questionable Measurement Practices

This study seeks to conceptually replicate some of the findings of @flake2022construct about QMP reporting in the RPP within the Many Labs replication projects.

-   RQ4a. To what degree are QMPs present in replications of psychological research?
-   RQ4b. To what degree are QMPs present in original psychological research?

@flake2022construct coded the presence of a series of QMPs in the replication report in both the replication protocols of each replication in the RPP, as well as the original articles the replications were based on. They found that not only are QMPs common in psychological research, they can be even more common in replications reports. However, the reporting of the Many Labs projects differ from the RPP data used in @flake2022construct. The structured and preregistered protocols used for the Many Labs projects were hypothesized to lead to consistent reporting of important measurement details, and as a result contain less QMPs.

-   H4. QMPs are expected to be more frequent in original psychological research than in replication research.

QMPs may obscure relevant information needed to evaluate the use of measurement in a study. If the replication used the measure differently from the original, the replication may no longer be a direct replication. ???link not direct replication to lack of replication through larger variance argument??? For these reasons, establishing a link between QMPs and non-replicability should confirm suspicions of their detrimental effects on replications [@flake2017construct; @flake2020measurement; @flake2022construct].

-   RQ5. What is the association between QMPs in replication studies and replication outcome?

Fewer QMPs means that measurement decisions in a report are transparent with the number arbitrary methodological decisions being limited as well. Fewer arbitrary decisions means less ways that a replicator can deviate from the original's intended effect. One of the Many Labs projects even touched on this concept [@ebersole2020many]. In this project, peer-review of replication protocols by original authors was used to ensure that approved methods were used. Additionally, it has been observed that authors who promote greater transparency in their work, have on average stronger evidence for their hypotheses [@wicherts2011willingness]. Finally, the results shown in @protzko2020high illustrate that when original studies are transparent, preregistered, and have adequate sample size, subsequent replication attempts find nearly the same effect size as the original. All of these findings point towards a positive relation between successful replication and various types of good research practices. A similar relation is expected for good measurement practices.

-   H5. QMPs in replication research are negatively associated with replication of an original finding.

This study additionally aims to see if the relation between QMPs and replicability can be traced back to original article QMPs. When essential information on a measure is not available in an original article, it may be difficult to know the specifics of that measure to report for a replication. Therefore this study also investigates the relation between original QMPs and replication QMPs.

-   RQ6. What is the association between QMPs in original research and QMPs in replications of psychological research?

If the relationship exists, it is expected that questionable measurement practices in an original paper might cause a spill-over effect of QMPs into the replication. @flake2022construct found that QMPs linked to issues for replicators in recreating the measurement to closely match the measurement in the original. As a result, there was a lack of measurement related information in both replication reports, and original articles. Additionally, investigations by @shaw2020measurement have shown that more validity evidence in an original article is associated with better psychometric properties in the replication sample. Based on these arguments, QMPs are expected to be associated across original and replication studies.

-   H6. Total number of QMPs in original psychological research is positively related to total number of QMPs in replication research.

# Method

Data collection, coding protocol, and planned analyses were all preregistered. The preregistration and supplementary materials can be found on this article's OSF page: <https://osf.io/9r8yt/>. Any deviations from the preregistration are explicitly mentioned in the text. This manuscript was generated using the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication.git>.

## Sample

The data used for the analyses in this study consists of three main sources: replication datasets, preregistered replication protocols, and original study articles. The data came from the Many Labs series of studies. In particular, data from Many Labs 1, 2, 3, & 5 was used [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many]. Data from Many Labs 4 [@klein2022many] was not part of the sample, as there was no publicly available protocol which contains the information needed to code QMPs. Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking as measures, which did not match this study's focus on scale and item measures.

The total number of psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of 60. Each finding was tested across several labs, and was related to a finding from an original study, the combination of all these studies and their associated information formed a replication set. For each research finding, any primary measures assessing a unique variable were taken to form the final unit of measurement. Here primary measures refers to measures assessing variables included in the primary test of the replication, were used. This was done to ensure that the analyses could link directly to the replicability of a study. Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included.. The result was a total sample size of 77 measures. The Table BELOW show descriptive information about the data for each Many Labs Project.

DESCRIPTIVE TABLE

(Row 1: Many Labs projects - 13 in Many Labs 1; 28 in Many Labs 2; 10 in Many Labs 3; & finally 9 out of the 10 tested findings in Many Labs 5)

(Row 2: Primary measures - 14 in Many Labs 1; 35 in Many Labs 2; 15 in Many Labs 3; & 13 in Many Labs 5)

(Row 3: ???)

Footnote about sample size differences between original and original shortened.

## Data Collection

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. When available, codebooks and study materials were used to identify the specific data for each measure.

### Replication Datasets

The replication datasets refer to the data of each of the replication attempts for each of the original psychological effects undertaken as part of a Many Labs study. These publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base] Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each relevant measure were extracted into their own data frame containing the data from all studies in one replication set. These pieces of information were used as the datasets in the analysis.

The measure had to consist of multiple scalar items to be considered relevant, as single item measures were not usable for the planned analyses on score reliability [@wanous1996estimating], which followed up on @stanley2014expectations simulation study. If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended. Pilot data were omitted from the analyses entirely. These criterion resulted in suitable measure data from eighteen replication sets spread across on average 40 lab locations for the analyses of hypotheses 2 & 3.

DESCRIPTIVE TABLE???

```{r CleaningReplicationDatasetsData, include = FALSE, eval = FALSE}
##### Data already available, code does not need to be run!
### ML 1
# 1.3
data_1.3_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[22:29])
colnames(data_1.3_clean)[1] <- "g"
# 1.10
data_1.10_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[108:115])
colnames(data_1.10_clean)[1] <- "g"
# 1.11
data_1.11_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[73:76])
colnames(data_1.11_clean)[1] <- "g"
# 1.12.1
# not found
# 1.12.3
data_1.12.3.1_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[54:59])
colnames(data_1.12.3.1_clean)[1] <- "g"
data_1.12.3.2_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[60:65])
colnames(data_1.12.3.2_clean)[1] <- "g"

### ML 2
# 2.2
data_2.2_clean <- cbind(as.factor(data_2.2[[5]]), data_2.2[6:11])
colnames(data_2.2_clean)[1] <- "g"
# 2.3
# data does not appear suitable
# 2.4.1
data_2.4.1_clean <- cbind(as.factor(data_2.4.1[[5]]), data_2.4.1[6:11])
colnames(data_2.4.1_clean)[1] <- "g"
# 2.4.2
data_2.4.2_clean <- cbind(as.factor(data_2.4.2[[5]]), data_2.4.2[6:14])
colnames(data_2.4.2_clean)[1] <- "g"
# 2.8.2
data_2.8.2_clean <- cbind(as.factor(data_2.8.2[[6]]), data_2.8.2[9:13])
colnames(data_2.8.2_clean)[1] <- "g"
# 2.10.1
data_2.10.1_clean <- cbind(as.factor(data_2.10.1[[5]]), data_2.10.1[6:11])
colnames(data_2.10.1_clean)[1] <- "g"
# 2.12.1
data_2.12.1_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(6,7,8,9,10,31,32,33,34,35)]) 
data_2.12.1_clean[3465:6905,2:6] <- data_2.12.1_clean[3465:6905,7:11]
data_2.12.1_clean <- data_2.12.1_clean[1:6]
colnames(data_2.12.1_clean)[1] <- "g"
# 2.12.2
data_2.12.2_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(11,14,15,18,19,22,24,27,28,29,36,39,40,43,44,47,49,52,53,54)]) 
data_2.12.2_clean[3465:6905,2:11] <- data_2.12.2_clean[3465:6905,12:21]
data_2.12.2_clean <- data_2.12.2_clean[1:11]
colnames(data_2.12.2_clean)[1] <- "g"
# 2.12.3
data_2.12.3_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(12,13,16,17,20,21,23,25,26,30,37,38,41,42,45,46,48,50,51,55)]) 
data_2.12.3_clean[3465:6905,2:11] <- data_2.12.3_clean[3465:6905,12:21]
data_2.12.3_clean <- data_2.12.3_clean[1:11]
colnames(data_2.12.3_clean)[1] <- "g"
# 2.15
data_2.15_clean <- cbind(as.factor(data_2.15[[5]]), data_2.15[8:12])
colnames(data_2.15_clean)[1] <- "g"
# 2.19.1
# difficult to extract
# 2.19.2
# difficult to extract
# 2.20
data_2.20_clean <- cbind(as.factor(data_2.20[[5]]), data_2.20[6:45]) 
data_2.20_clean[3729:7396,2:21] <- data_2.20_clean[3729:7396,22:41]
data_2.20_clean <- data_2.20_clean[1:21] 
# coding so all 1's means somebody used rule-based grouping strategy
data_2.20_clean[,c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20)] <- ifelse(data_2.20_clean[,c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20)] == 1, 1, 0)
data_2.20_clean[,c(3, 5, 7, 9, 11, 13, 15, 17, 19, 21)] <- ifelse(data_2.20_clean[,c(3, 5, 7, 9, 11, 13, 15, 17, 19, 21)] == 2, 1, 0)
colnames(data_2.20_clean)[1] <- "g"
# 2.23
data_2.23_clean <- cbind(as.factor(data_2.23[[5]]), data_2.23[c(7,8,12,13,15)])
colnames(data_2.23_clean)[1] <- "g"

### ML 3
# 3.2.1
data_3.2.1 <- cbind(as.factor(data_ml3[[1]]), data_ml3[77:86] - 1)
data_3.2.1.1_clean <- na.omit(data_3.2.1[1:6])
colnames(data_3.2.1.1_clean)[1] <- "g"
data_3.2.1.2_clean <- na.omit(data_3.2.1[c(1, 7:11)])
colnames(data_3.2.1.2_clean)[1] <- "g"
# 3.5
# data appears unusable
# 3.7.1
data_3.7.1_clean <- na.omit(cbind(as.factor(data_ml3[[1]]), data_ml3[38:42]))
colnames(data_3.7.1_clean)[1] <- "g"
# 3.7.2
data_3.7.2_clean <- na.omit(cbind(as.factor(data_ml3[[1]]), data_ml3[89:94]))
colnames(data_3.7.2_clean)[1] <- "g"
# 3.8.1
# a single measure was reported
# 3.8.2
data_3.8.2_clean <- na.omit(cbind(as.factor(data_ml3[[1]]), data_ml3[29:30])) 
colnames(data_3.8.2_clean)[1] <- "g"

### ML 5
# 5.1.1
data_5.1.1_clean <- cbind(as.factor(data_5.1[[2]]), data_5.1[13:27])
colnames(data_5.1.1_clean)[1] <- "g"
# 5.1.2
data_5.1.2_clean <- cbind(as.factor(data_5.1[[2]]), data_5.1[28:33])
colnames(data_5.1.2_clean)[1] <- "g"
# 5.4
data_5.4_clean <- cbind(as.factor(data_5.4[[1]]), data_5.4[18:41])
colnames(data_5.4_clean)[1] <- "g"
# 5.5.1 & 5.5.2
# from this dataset it appears that this data will be difficult to use.
# 5.5.2
# also difficult to use
# 5.7 
data_5.7_clean <- cbind(as.factor(data_5.7[[3]]), data_5.7[c(25, 34, 35, 36, 37, 38, 39, 40, 41, 42)])
colnames(data_5.7_clean)[1] <- "g"
# 5.9.1
data_5.9.1_clean <- na.omit(cbind(as.factor(data_5.9.1[[4]]), data_5.9.1[c(79, 83, 87, 91, 95, 98, 101)]))
colnames(data_5.9.1_clean)[1] <- "g"

### to summarize
# total number of likely usable: 15 (1.10, 1.11, 1.12.3.1, 1.12.3.2, 2.10.1, 
# 2.12.1, 2.12.2, 2.12.3, 2.15, 2.23, 3.7.1, 3.7.2, 3.8.2, 5.7, 5.9.1)
# total number of maybe usable: 6 (1.3, 2.20, 3.2.1.1, 3.2.1.2, 5.1.1, 5.4)
# total alpha coefficient comparison usable: 3 
#                                           1.11: 0.82
#                                           3.7.2: 0.67
#                                           5.9.1: 0.84

### Saving to Intermediate Data Folder
open_data(data = data_1.3_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_1.3_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_1.3_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_1.3_clean))), ".yml"))

open_data(data = data_1.10_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_1.10_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_1.10_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_1.10_clean))), ".yml"))

open_data(data = data_1.11_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_1.11_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_1.11_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_1.11_clean))), ".yml"))

open_data(data = data_1.12.3.1_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_1.12.3.1_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_1.12.3.1_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_1.12.3.1_clean))), ".yml"))

open_data(data = data_1.12.3.2_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_1.12.3.2_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_1.12.3.2_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_1.12.3.2_clean))), ".yml"))

open_data(data = data_2.10.1_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_2.10.1_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_2.10.1_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_2.10.1_clean))), ".yml"))

open_data(data = data_2.12.1_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_2.12.1_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_2.12.1_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_2.12.1_clean))), ".yml"))

open_data(data = data_2.12.2_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_2.12.2_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_2.12.2_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_2.12.2_clean))), ".yml"))

open_data(data = data_2.12.3_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_2.12.3_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_2.12.3_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_2.12.3_clean))), ".yml"))

open_data(data = data_2.15_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_2.15_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_2.15_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_2.15_clean))), ".yml"))

open_data(data = data_2.20_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_2.20_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_2.20_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_2.20_clean))), ".yml"))

open_data(data = data_2.23_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_2.23_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_2.23_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_2.23_clean))), ".yml"))

open_data(data = data_3.2.1.1_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_3.2.1.1_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_3.2.1.1_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_3.2.1.1_clean))), ".yml"))

>>>>

# Appendix A

```{r setup, include=FALSE}
# loading R libraries, perhaps unnecessary
library(papaja)

# loading source script, perhaps unnecessary
source(file = "C:/Users/u686785/OneDrive - Tilburg University/Documents/uvt/PHD/Master Thesis to Paper/Reproducible_R_Project/Scripts/source_script.R")

@@

This appendix contains all of the pre-registered analyses that were either changed or omitted from the article.

## Test for H5 as Beta-Regression

### Explanation Change

This analysis was the originally planned analysis to test Hypothesis 5. However, for the sake of interpretation this test was changed to have the Independent Variable (IV) and Dependent Variable (DV) swapped in the article, and as a result it became a logistic regression.

### Model

The originally planned analysis made use of beta-regression similarly to the test for H4 and H6. The variables are the same as those used in the test published in the article, just swapped from IV to DV, and from DV to IV.

```{=tex}
\begin{equation}
g(QMP\_ratio_{i}) = \beta_{0} + \beta_{1} replicated_{i} (\#eq:H5AppendixA)
\end{equation}
```
Where $g(.)$ refers to the same link function as described in formula \@ref(eq:BetaLink) in the article.

```{r H5 beta-regression pre-registration model}
## Hypothesis 5 beta regression model ADD FIRST PART TO INITIAL PROTOCOL RESULTS
H5_prereg_test_results <- betareg(QMP_ratio ~ hypothesis_support, data = data_h5)
H5_prereg_test_results_with_OR <- OR_to_apa_full_supplier(betareg_output_to_apa_full(H5_prereg_test_results), negative_b = TRUE)

H5_prereg_test_results_REV <- betareg(QMP_REV_ratio ~ hypothesis_support, data = data_h5)
H5_prereg_test_results_REV_with_OR <- OR_to_apa_full_supplier(betareg_output_to_apa_full(H5_prereg_test_results_REV))
```

## Results

With this model specification the relationship between the two variables remains negative and significant (`r H5_prereg_test_results_REV_with_OR`).

## Unidimensionality Exploratory Analyses

### Pre-registration Analysis Justification & Reason for Omission from Article

In order to present additional validity evidence alongside the analyses of Cronbach's alpha and omega coefficients, the unidimensionality of each measure was investigated. To test this, each multiple item scalar measure had their factor structure investigated on the entire measure data of the replication set.

This analysis was omitted from the main article due to the fact that determining when a measure should be unidimensional would require an in-depth review and expert evaluation for the literature surrounding the measure, which is outside of the scope of this article and the authors' expertise (it additionally may not always be available).

For the sake of this analysis the simple heuristic was chosen that if the measure was used as a single composite variable in the analyses, then it should be uni-dimensional. This is similar to what was done by ..., but for the sake of this article it was deemed to strong an assumption to make that this heuristic would always hold. For instance, IQ score is often used as a single indicator score, however the construct of IQ is not considered unidimensional, and is instead understood to have many sub-dimensions (e.g. verbal comprehension, perceptual reasoning, etc.). As a result, the use of a single score in the analyses cannot be taken as evidence that the construct is considered unidimensional by the authors, or broader literature on the topic.

Nevertheless, we present here the result of the analyses made under the assumption that the one score, one dimension heuristic holds, for those researchers that believe this heuristic to not undermine the relevance of these results in provding some valid information on the validity of the measures used in the Many Labs projects.

## models

A single factor confirmatory factor analysis was implemented using the *fa* function from the *psych* package [@R-psych] in R. The maximum likelihood factoring method was used, with defaults being used for all other function arguments. From this analysis, the RMSEA of the one factor solution was extracted. Additionally, a parallel test was conducted using the *fa.parallel* function also from the psych package. If either the RMSEA score \< .08, or the parallel analysis returned a one factor solution, unidimensionality was coded as true, otherwise it was coded as false.

```{r UnidimensionalityExploratoryAnalysis, include = FALSE}
extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, data_1.12.3.2_clean,data_2.12.1_clean, data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean, data_3.7.2_clean, data_3.8.2_clean, data_5.1.1_clean, data_5.1.2_clean, data_5.7_clean, data_5.9.1_clean)
